### 2020-12-19 README.Rmd
fix some things, add create_statedays()

- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

>>>>

- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format
- `create_statedays()`: converts Correlates of War or Gleditsch-Ward state membership data into state-day format..
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.
